Formalization, Mechanization and Automation of \\ G\"{o}del's Proof of God's Existence

### 2013-10-30 Talks/FU-Berlin/talk-part-1.tex
new Isabelle/HOL version of the proof
update of FU talk
Add "Die Presse"

\begin{frame}{Introduction} \small
\begin{minipage}{.56\textwidth} 
\includegraphics[width=\textwidth]{spiegel1} 
\vskip1em
Germany \\
- Telepolis \& Heise \\
- Spiegel Online \\
- FAZ \\
- Die Welt \\
- Berliner Morgenpost \\
- Hamburger Abendpost \\
- \ldots \\
\end{minipage} \hfill
%
\begin{minipage}{.3\textwidth}
Austria \\
- myscience.at \\
- Wiener Zeitung \\
- ORF \\
- \ldots \\

@@

India \\
- DNA India \\
- Delhi Daily News \\
- Indoa Today \\
- \ldots \\

>>>>

\begin{frame}{Introduction} \small
\begin{minipage}{.56\textwidth} 
\includegraphics[width=\textwidth]{spiegel1} 
\vskip1em
Germany \\
- Telepolis \& Heise \\
- Spiegel Online \\
- FAZ \\
- Die Welt \\
- Berliner Morgenpost \\
- Hamburger Abendpost \\
- \ldots \\
\end{minipage} \hfill
%
\begin{minipage}{.3\textwidth}
Austria \\
- Die Presse \\
- Wiener Zeitung \\
- ORF \\
- \ldots \\

@@

India \\
- DNA India \\
- Delhi Daily News \\
- India Today \\
- \ldots \\
